### 2017-12-20 chapters/introduction/summary.tex
Fix some final typos

Regarding the mechanical modeling of the heart, 
\emph{choosing appropriate boundary conditions} that reflect the reality has
been an issue during the work of this thesis, and several different
choices has been made. Moreover, \emph{accounting for the orthotropic as
well as the visco-elastic behavior of the myocardium} is something that should
be investigated in future studies. Accounting for an orthotropic
behavior would acquire more parameters to be estimated, which would
thus require more input data.
In this thesis we have also not fully
explored the \emph{spatial resolution of the material parameters}, and it
should be investigated whether it is possible to relate locally estimated
tissue stiffness to e.g myocardial infarction.
% The choice of active model for the myocardium is another topic that
% should be addressed in more detail in future studies. In the author's
% opinion, the output of the two fundamentally different approaches may
% vary a lot. In particular, it is evident that the active strain
% formulation do a better job in fitting strain data. One
% hypothesis is that the amount of transverse active stresses should be
% adjusted to each individual. These transverse active stresses are
% naturally embedded in the active strain approach via a volume
% preserving active deformation.

>>>>

Regarding the mechanical modeling of the heart, 
\emph{choosing appropriate boundary conditions} that reflect the reality has
been an issue during the work of this thesis, and several different
choices have been made. Moreover, \emph{accounting for the orthotropic as
well as the visco-elastic behavior of the myocardium} is something that should
be investigated in future studies. Accounting for an orthotropic
behavior would acquire more parameters to be estimated, which would
thus require more input data.
In this thesis we have also not fully
explored the \emph{spatial resolution of the material parameters}, and it
should be investigated whether it is possible to relate locally estimated
tissue stiffness to e.g myocardial infarction.
% The choice of active model for the myocardium is another topic that
% should be addressed in more detail in future studies. In the author's
% opinion, the output of the two fundamentally different approaches may
% vary a lot. In particular, it is evident that the active strain
% formulation do a better job in fitting strain data. One
% hypothesis is that the amount of transverse active stresses should be
% adjusted to each individual. These transverse active stresses are
% naturally embedded in the active strain approach via a volume
% preserving active deformation.
